\documentclass[letterpaper,article,oneside]{memoir}
\setsecnumdepth{subsubsection}
\counterwithout{section}{chapter}

\usepackage[nopostdot]{glossaries}
\usepackage{graphicx}
\usepackage{ulem}
\usepackage{xspace}
\usepackage[dvipsnames,svgnames]{xcolor}
\usepackage[utf8]{inputenx}
\usepackage[margin=2cm]{geometry}
\usepackage{subfig}
\usepackage{siunitx}
\usepackage{hyperref}

\setglossarystyle{index}
\input{daq-glossary}

\title{DUNE FD DAQ Glossary}
%\author{Brett Viren}
\date{\today}


\begin{document}
\maketitle

\tableofcontents*

\section{Introduction}
\label{sec:intro}

The DUNE Far Detector DAQ is composed of many parts performing
specific roles by transmitting data streams and discrete messages of
specific type. 
These parts and messages must operate in concert. 
In order to discus, describe and develop the DAQ design a shared
vocabulary is needed in order to avoid chaotic babel.

This glossary serves as a reference and specification for the terms of
that vocabulary.
A design language it must of course reflect the design itself and thus
shall evolve as the design evolves. 
This glossary of this document shall be merged into the DUNE Technical
Design Report. 
The glossary in this document shall be revised as required to follow
design evolution subsequent to the TDR completion and it shall be
expanded as the DAQ design is implemented and new terms are needed to
cover concrete systems, parts and messages.

\section{Verboten and Generic Terms}

Here we give a short ``anti glossary'' of terms that shall be avoided
(verboten), called out as generic or otherwise are listed to highlight
potential ambiguity.

to call
attention to potential ambiguity.
These terms, spoken in isolation, typically have meanings which are
ambiguous and lead to more confusion than clarity. 
Used with sufficient qualifiers they may be legal terms in the
vocabulary.
However, they are sometimes used more formally but with a lack of
clarity. 
They are also explicitly listed so that the vocabulary may take care
to avoid using them in an ambiguous manner.


\begin{description}
\item[\sout{event}] This term has many context-dependent meanings and
  in some contexts even those meanings are ambiguous. 
  The term \sout{event} is particularly ambiguous in the case of
  detectors such as DUNE FD where there are many particle interactions
  in a subset of data output by the DAQ.
  The DAQ vocabulary will explicitly
  refrain from using this term to describe any occurrence in space or
  time or to refer to any subset of the DAQ \gls{daq:datastream}. 
  As an occurrence, various related vocabulary terms are defined:
  \gls{daq:actdesc}, \gls{daq:tp}, \gls{daq:tc} and \gls{daq:ta}. 
  As a subset of data, related terms are: \gls{daq:datafrag} and
  \gls{daq:datablock}. 
  However, to accommodate established nomenclature, this term is
  explicitly used as a modifier to name \gls{daq:eb} component.
\item[\sout{readout}] Unqualified, the term \gls{daq:readout} is used
  generically. 
  Modified, it is used vocabulary terms: \gls{daq:fer}.
\item[\sout{trigger}] This word is used as a modifier in several vocabulary
  terms related to the process of \gls{daq:ds}. 
  They are: \gls{daq:tp}, \gls{daq:tc}, \gls{daq:ta}. 
  In written prose the unqualified term shall be avoided. 
  In informal dialog (or where avoidance fails) it shall be considered
  a synonym for \gls{daq:ta}.
\end{description}


\section{Glossary Conventions}

The glossary covers:

\begin{description}
\item[verbs] The major functions of the DAQ are in the form of active verbs.
\item[nouns] Conceptual elements are in the form of general nouns.
\item[Proper Noun] Explicitly named components and subsystems are capitalized as proper nouns.
\item[abbreviations] Some commonly used terms are given parenthetical abbreviations.
\end{description}

% \printglossaries
\printnoidxglossary[type=daq]

\glsaddallunused

\end{document}